Using NSGA-II to compose model transformations alternatives

### 2014-10-30 SysCon_article/article_syscon.tex
modification of all the paper

\subsection{Mapping model transformation alternatives into a multiple-objectives optimization problem}
\label{Adapting}

The next step of our approach consist in using model transformations definitions described in Section~\ref{transfos} and integrate them into a multiple-objectives optimization problem. Where the population to optimize or the design space represent a set of model transformations alternatives and the objectives to fulfils are NFP such as reliability, availability and response time. The integration process is described in the following sections.

%In this paper we propose a generic method to automate the search of optimal architectures (which fulfil at best the NFP of the system) from the design space. To represent the design space (set of architecture alternatives) we use model transformations compositions. The exploration step is done by using the NSGA-II algorithm.

\subsubsection{\textbf{Genome representation}}

@@

\section{Acknowledgment}
This research work has been carried out under the leadership of the Technological Research Institute SystemX, and therefore granted with public funds within the scope of the French Program "Investissements d’Avenir".

>>>>

\subsection{Mapping model transformation alternatives into a multiple-objectives optimization problem}
\label{Adapting}
The next step of our approach consist in using model transformations definitions described in Section~\ref{transfos} and integrate them into a multiple-objectives optimization problem. Where the population to optimize or the design space represent a set of model transformations alternatives and the objectives to fulfils are NFP such as reliability, availability and response time. The integration process is described in the following sections.
\subsubsection{\textbf{Genome representation}}

@@

\section{Acknowledgment}
This research work has been carried out under the leadership of the Technological Research Institute SystemX, and therefore granted with public funds within the scope of the French Program ``Investissements d'Avenir''.
